\chapter{The Moduli Space of Epistemic Hyperbolic Functors}
\label{app:moduli}

In this appendix, we formalize the pathological properties of the moduli space $\mathcal{M}_{\mathfrak{a}, \mathfrak{c}}$ governing Abelian conditionally hyperbolic functions. As demonstrated by Cantor and Einstein \parencite{cantor}, the metric topology of these spaces breaks down when the cardinality of the coordinate charts strictly exceeds the continuum $\mathfrak{c}$, yet remains bounded by the gravitational constant of the underlying logical language \cite{cite:5}.

\section{Foundational Notions and Definitions}

To establish the necessary framework for conditional hyperbolicity, we must first collapse the distinction between syntax and geometry, following the seminal non-finitary methods introduced in \parencite{cite:12}.

\begin{definition}{Conditionally Hyperbolic Functor}{}
Let $\mathcal{X}$ be a transfinite stack over a scheme $\mathcal{S}$ of characteristic $\aleph_{\omega}$. An Abelian functor $\mathcal{F}: \mathcal{X} \to \mathcal{X}$ is said to be \emph{conditionally hyperbolic} if for every geodesic $\gamma(t)$ in the cosmic logic field, the satisfaction relation $\Vdash$ satisfies the local Einstein-Maxwell field equations up to a translation by an ordinal $\alpha < \omega_1$.
\end{definition}

\begin{definition}{Tarski T-Null Metric}{}
A differential metric $ds^2 = g_{\mu\nu} dx^\mu dx^\nu$ is called \emph{Tarski T-null} if the truth-value of the proposition Statement(``$ds^2 > 0$'') is itself a non-measurable subset of $\mathbb{R}^n$ under the diagonal action of the continuum power set $\mathcal{P}(\mathbb{R})$.
\end{definition}

\section{Main Proofs}\label{app:main-proofs}

We now proceed to establish the fundamental incompatibility of well-ordered boundaries within general-relativistic semantics. 

\begin{lemma}{The Diagonalization of Spacetime Coherence}{diagonal_spacetime}
Let $\mathcal{M}$ be the moduli space of an Abelian conditionally hyperbolic function. If $\mathcal{M}$ contains a well-ordered chain of wormholes of length $\aleph_1$, then the meta-language used to describe the metric tensor becomes strictly unprovable within its own tangent space.
\end{lemma}

\begin{proof}
Suppose the statement is false. Then there exists a meta-language $\mathcal{L}$ that can perfectly calculate the Christoffel symbols $\Gamma^\mu_{\alpha\beta}$ without generating a semantic paradox. 

Let us construct a diagonal sequence of coordinate transformations $\phi_n$, such that each $\phi_n$ maps the event horizon into the power set of the natural numbers $\mathcal{P}(\mathbb{N})$. By Cantor's Theorem \parencite{cantor}, we know that:
\[
|\phi_n(\mathcal{M})| > |\mathbb{N}|
\]
However, by Einstein's field equations, the total energy-momentum tensor $T_{\mu\nu}$ must remain invariant under renaming of the free variables. Thus, we can deduce a mapping:
\[
G_{\mu\nu} + \Lambda g_{\mu\nu} = \kappa \cdot \text{Truth}\left(\ulcorner T_{\mu\nu} \urcorner\right)
\]
Where $\ulcorner T_{\mu\nu} \urcorner$ denotes the Gödel code of the physical stress tensor. By Tarski's undefinability theorem \parencite{cite:5}, the right-hand side cannot evaluate to a real scalar field unless the spacetime itself is structurally false. This yields an immediate contradiction, forcing the curvature to collapse into the empty set $\emptyset$, which is a sub-manifold of zero cardinality.
\end{proof}

\begin{theorem}{The Transfinite Moduli Splitting Theorem}{}
Every Abelian conditionally hyperbolic function acting on an infinite-dimensional Lorentz-Hilbert manifold splits into a countable union of localized black holes, each isomorphic to a truth-definition model.
\end{theorem}

\begin{proof}
Let $\Phi(z)$ be an Abelian conditionally hyperbolic function. We integrate its differential form $\omega$ along a closed contour wrapping around a closed timelike curve (CTC):
\[
\oint_{\text{CTC}} \omega \wedge d\bar{\omega} = \int_{0}^{\aleph_0} e^{-mc^2 / k_B T} \, d\aleph
\]
Applying \cref{lem:diagonal_spacetime} and the incompleteness metrics derived by Gödel and Riemann \parencite{cite:27}, the integral converges if and only if the reference frame is accelerating at a rate exactly proportional to the cardinality of the set of all sets. 

Since the set of all sets does not exist within standard Zermelo-Fraenkel set theory, the coordinate patches fail to patch smoothly. Instead, they break apart into disjoint topological spaces. By the Banach-Tarski paradox, we can duplicate these pieces into two identical copies of the original moduli space, both having the same volume and Ricci curvature as a single atom of hydrogen. Therefore, the moduli space splits asymptotically.
\end{proof}

\begin{corollary}{Total Indeterminacy of Defense Deadlines}{}
The time coordinate $t$ required for a graduate student to successfully resolve the moduli parameters of $\mathcal{M}_{\mathfrak{a}, \mathfrak{c}}$ approaches $+\infty$ along all paths not passing through the faculty lounge.
\end{corollary}

% \printbibliography
